Scalable and Parameter-Free Exploration in Deep Reinforcement Learning

### 2022-01-10 papers/main.tex
TEMPORARY DEPLOY COMMIT

In NoisyNet \citep{fortunato_noisy_2019}, the Q-function space can be seen
as a stochastic process on the probability space \((\Omega, \mathcal{F}, P)\).
The stochastic process can simply be written as
\(\{Q(\bm{s}, \bm{a}) : (\bm{s}, \bm{a}) \in \state \times \action \}\). For
any \(\omega \in \Omega\), \(Q(\cdot, \cdot, \omega)\) is a sample function
mapping \(\state \times \action \rightarrow \mathbb{R}\). To simplify notation
we will denote sample functions as \(f\). NoisyNet, specifically, is a stochastic
process parameterized by its weights and their standard deviation. We will define
this parameterized function as \(g_\phi\), and their sampling distribution as
\(q_\phi \in \mathcal{Q}\). Given a noise vector \(\xi\), we have
\(f(\bm{s}, \bm{a}) = g_\phi(\bm{a}, \bm{s}, \xi)\).

@@

\textcolor{red}{A natural step for finding
the optimal sampling distribution \(q_\phi\) is to minimize the KL-divergence
between it and the true Q-value function. This is different from the optimization
scheme in NoisyNet, which only tries to maximize the likelihood that samples from
\(q_\phi\) comes from the true Q-value function.}

>>>>

In NoisyNet \citep{fortunato_noisy_2019}, the Q-function space can be seen
as a stochastic process on the probability space \((\Omega, \mathcal{F}, P)\).
The stochastic process can simply be written as
\(\{Q(\bm{s}, \bm{a}) : (\bm{s}, \bm{a}) \in \state \times \action \}\). For
any \(\omega \in \Omega\), \(Q(\cdot, \cdot, \omega)\) is a sample function
mapping \(\state \times \action \rightarrow \mathbb{R}\). To simplify notation
we will denote sample functions as \(f\). NoisyNet, specifically, is a stochastic
process parameterized by its weights and their standard deviation. We will define
this parameterized function as \(g_\phi\), and their sampling distribution as
\(q_\phi \in \mathcal{Q}\). Given a noise vector \(\xi\), we have
\(f(\bm{s}, \bm{a}) = g_\phi(\bm{a}, \bm{s}, \xi)\). This means that NoisyNet
gives a new policy function for each noise vector \(\xi\).

@@

% A natural step for finding
% the optimal sampling distribution \(q_\phi\) is to minimize the KL-divergence
% between it and the true Q-value function. This is different from the optimization
% scheme in NoisyNet, which only tries to maximize the likelihood that samples from
% \(q_\phi\) comes from the true Q-value function.
